The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-03 paper.tex
update

We perform three-dimensional special relativistic hydrodynamics simulations\
of the formation of the Galactic bubbles by CR jet injections\
from the central SMBH in the Galaxy.

>>>>

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the jet scenario is able to produce symmetric Galactic bubbles that are\
consistent with the observed features, including the shape, the\
flat surface brightness, and the sharp edges.\
